iSEE: Interactive SummarizedExperiment Explorer

### 2018-05-05 manuscript/main.tex

\title{iSEE: Interactive SummarizedExperiment Explorer}
\author[1,$\dagger$]{Kevin Rue-Albrecht}
\author[2,3,$\dagger$]{Federico Marini}
\author[4,5,$\dagger$]{Charlotte Soneson}
\author[6,$\dagger$,$\ast$]{Aaron T. L. Lun}

\affil[1]{Kennedy Institute of Rheumatology, University of Oxford, Oxford OX3 7FY, United Kingdom}
\affil[2]{Center for Thrombosis and Hemostasis (CTH), University Medical Center of the Johannes Gutenberg University Mainz, Mainz}
\affil[3]{Institute for Medical Biostatistics, Epidemiology and Informatics (IMBEI), University Medical Center of the Johannes Gutenberg University Mainz, Mainz}
\affil[4]{Institute of Molecular Life Sciences, University of Zurich, 8057 Zurich, Switzerland}
\affil[5]{SIB Swiss Institute of Bioinformatics, University of Zurich, 8057 Zurich, Switzerland}
\affil[6]{Cancer Research UK Cambridge Institute, University of Cambridge, Cambridge CB2 0RE, United Kingdom}
\affil[$\dagger$]{These authors contributed equally.}
\affil[$\ast$]{To whom correspondence should be addressed.}

>>>>

\title{iSEE: Interactive SummarizedExperiment Explorer}
\author[1,$\dagger$]{Kevin Rue-Albrecht}
\author[2,3,$\dagger$]{Federico Marini}
\author[4,$\dagger$]{Charlotte Soneson}
\author[5,$\dagger$,$\ast$]{Aaron T. L. Lun}

\affil[1]{Kennedy Institute of Rheumatology, University of Oxford, Oxford OX3 7FY, United Kingdom}
\affil[2]{Center for Thrombosis and Hemostasis (CTH), University Medical Center of the Johannes Gutenberg University Mainz, Mainz}
\affil[3]{Institute for Medical Biostatistics, Epidemiology and Informatics (IMBEI), University Medical Center of the Johannes Gutenberg University Mainz, Mainz}
\affil[4]{University of Zurich and SIB Swiss Institute of Bioinformatics, Zurich, Switzerland}
\affil[5]{Cancer Research UK Cambridge Institute, University of Cambridge, Cambridge CB2 0RE, United Kingdom}
\affil[$\dagger$]{These authors contributed equally.}
\affil[$\ast$]{To whom correspondence should be addressed.}
